---
title: "BOPS_Analysis"
author: "Jiying Lu"
date: "3/22/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Set up environment
```{r}
rm(list = ls())
setwd("/Users/lucute/Desktop/Side Project/BOPS_R")
ca <- read.csv(file.choose())
b12 <- read.csv(file.choose())
b12$X <- NULL
b13 <- read.csv(file.choose())
b13$X <- NULL

library(stringr)
library(data.table)
library(MASS)
library(foreign)
library(gplots)
library(lmtest)
library(usdm)
library(sandwich)
library(plyr)
library(ggplot2)
install.packages("effects")
library(effects)
install.packages("interplot")
library(interplot)
install.packages("jtools")
library(jtools)
```

#Generate bops12 and bops13 column to indicate whether this transaction happen after adopting bops or not
```{r}
ca$year_month <- paste(ca$year, ca$month, sep = "")
?substr
ca$date <- substr(ca$purchase_date, 1,9)

ca$bops12 <- ifelse((ca$year == 2011 & ca$month %in% c("AUG","SEP","OCT","NOV","DEC") & ca$store_number %in% c(2,6)) | (ca$year %in% c(2012,2013) & ca$store_number %in% c(2,6)),1,0)

ca$bops13 <- ifelse(ca$bops12 == 1 | (ca$year == 2012 & ca$month %in% c("OCT", "NOV", "DEC") & ca$store_number == 5998) | (ca$year == 2013 & ca$store_number == 5998) | (ca$year == 2012 & ca$date %in% c("27SEP2012", "28SEP2012", "29SEP2012", "30SEP2012" )),1,0)

ca$bops <- ifelse((ca$bops12 == 1) | (ca$bops13 == 1),1,0)

count(ca$bops)
count(ca$bops12)
count(ca$bops13)
count(ca$bops13[ca$store_number == 5998])

```

Generate dummy variables for whether using bops or not
```{r}
ca$usebops12 <- ifelse(ca$transaction_id %in% b12$transaction_id,1,0)
ca$usebops13 <- ifelse(ca$transaction_id %in% b13$transaction_id,1,0)

count(ca$usebops12)
count(ca$usebops13)

#Export to csv:
write.csv(ca, file = "ca.txt")
ca <- read.csv(file.choose())
ca$X <- NULL

```

#Q1: What is the impact of adopting BOPS strategy on online channel sales/returns?
Analysis strategy:
By store -> compare the impact on sales for each store

subset the data
```{r}
cas2 <- ca[ca$store_number == 2,]
cas6 <- ca[ca$store_number == 6,]
cas5998 <- ca[ca$store_number == 5998,]
```

cas2
check data
```{r}
dim(cas2)
str(cas2)
count(cas2, var = "bops")
count(cas2, var = "gender")
count(cas2, var = "ethnic_code")
count(cas2, var = "homeowner_code")

hist(cas2$net_purchase_amount)
hist(log(cas2$net_purchase_amount +1))
cas2$logamount <- log(cas2$net_purchase_amount +1)

hist(cas2$age_band)
hist(cas2$est_income_code)
hist(cas2$length_of_residence)

cor <- cbind(cas2[,c(5,12,13,16)])
cor <- na.omit(cor)
cor2 <- cor(cor)
vif(cor)

sum(is.na(cas2))
colSums(is.na(cas2))

#replace NA with mean for columns age_band, est_income_code, and length_of_residence
cas2$age_band[is.na(cas2$age_band)] <- mean(cas2$age_band, na.rm = TRUE)
cas2$est_income_code[is.na(cas2$est_income_code)] <- mean(cas2$est_income_code, na.rm = TRUE)
cas2$length_of_residence[is.na(cas2$length_of_residence)] <- mean(cas2$length_of_residence, na.rm = TRUE)

unique(cas2$homeowner_code)
cas2$homeowner_code <- sub("^$", "N", cas2$homeowner_code)

#Same for the gender
cas2$gender <- sub("^$", "U", cas2$gender)
unique(cas2$gender)

unique(cas2$child)
count(cas2$child)
cas2$child <- sub("^$", "U", cas2$child)

colSums(is.na(cas2))

#drop 4 rows with summary na

cas2 <- cas2[!is.na(cas2$summary),]



```

Modeling
```{r}
cas2_1 <- lm(cas2$logamount ~ factor(cas2$gender) + cas2$age_band + cas2$est_income_code + factor(cas2$ethnic_code) + cas2$length_of_residence + factor(cas2$child) + factor(cas2$homeowner_code) + relevel(cas2$month, ref = "JAN") + cas2$bops)
summary(cas2_1)
AIC(cas2_1) #4816761
dwtest(cas2_1) #With p-value greater than 0.05, we have 95% confidence to accept null hypothesis!

#The estimation for homeowner_code R is NA, probable reasons are 1) Collinearity with ohter variables 2) too less observations
count(cas2, var = "homeowner_code") #Looks like it is not because of too less observations
# R = total amount - (N+O), since N is not the crucial option among O,R,and N. So I decided to set the reference to O.

cas2_1_2 <- lm(cas2$logamount ~ factor(cas2$gender) + cas2$age_band + cas2$est_income_code + factor(cas2$ethnic_code) + cas2$length_of_residence + factor(cas2$child) + relevel(factor(cas2$homeowner_code), ref = "O" ) + relevel(cas2$month, ref = "JAN") + cas2$bops)
summary(cas2_1_2)

#Now I have the estimate for R compares to O


#Add month index for capturing time trend in this data
cas2_2 <- lm(cas2$logamount ~ factor(cas2$gender) + cas2$age_band + cas2$est_income_code + factor(cas2$ethnic_code) + cas2$length_of_residence + factor(cas2$child) + relevel(factor(cas2$homeowner_code), ref = "O" ) + relevel(cas2$month, ref = "JAN") + cas2$bops + cas2$month_index)
summary(cas2_2)
AIC(cas2_2) #4807411
dwtest(cas2_2) #1.4821 a liitle closer to 2 than last model

#Add summary variable
cas2_3 <- lm(cas2$logamount ~ relevel(factor(cas2$gender), ref = "U") + cas2$age_band + cas2$est_income_code + factor(cas2$ethnic_code) + cas2$length_of_residence + relevel(factor(cas2$child), ref = "U") + relevel(factor(cas2$homeowner_code), ref = "O" ) + relevel(cas2$month, ref = "JAN") + cas2$bops + cas2$month_index + factor(cas2$summary))
summary(cas2_3)
AIC(cas2_3) #4155421
dwtest(cas2_3) #1.5818

#Drop ethinic_code

cas2_4 <- lm(cas2$logamount ~ relevel(factor(cas2$gender), ref = "U") + cas2$age_band + cas2$est_income_code + cas2$length_of_residence + relevel(factor(cas2$child), ref = "U") + relevel(factor(cas2$homeowner_code), ref = "O" ) + relevel(cas2$month, ref = "JAN") + cas2$bops + cas2$month_index + factor(cas2$summary))
summary(cas2_4)
AIC(cas2_4) #4157670
dwtest(cas2_4) #1.5798

#For the age band, we have positive sign for estimate, how about quadratic age band?
plot(cas2$net_purchase_amount ,cas2$age_band)

cas2_5 <- lm(cas2$logamount ~ relevel(factor(cas2$gender), ref = "U") + cas2$age_band + I(cas2$age_band^2) + cas2$est_income_code + cas2$length_of_residence + relevel(factor(cas2$child), ref = "U") + relevel(factor(cas2$homeowner_code), ref = "O" ) + relevel(cas2$month, ref = "JAN") + cas2$bops + cas2$month_index + factor(cas2$summary))
summary(cas2_5)
AIC(cas2_5) #4157578
dwtest(cas2_5) #1.5798
anova(cas2_4, cas2_5, test = "Chisq") #Model fit improves with the quadratic variable
bptest(cas2_5) 

#BOPS and Summary
cas2_6 <- lm(cas2$logamount ~ relevel(factor(cas2$gender), ref = "U") + cas2$age_band + I(cas2$age_band^2) + cas2$est_income_code + cas2$length_of_residence + relevel(factor(cas2$child), ref = "U") + relevel(factor(cas2$homeowner_code), ref = "O" ) + relevel(cas2$month, ref = "JAN") + cas2$bops*factor(cas2$summary) + cas2$month_index + factor(cas2$summary))
summary(cas2_6)
AIC(cas2_6) #4163559 #Interaction terms doesn't seem to improve the model fit
dwtest(cas2_6) #1.5798

cas2_7 <- lm(cas2$logamount ~ relevel(factor(cas2$gender), ref = "U") + cas2$age_band + I(cas2$age_band^2) + cas2$est_income_code + cas2$length_of_residence + relevel(factor(cas2$child), ref = "U") + relevel(factor(cas2$homeowner_code), ref = "O" ) + relevel(cas2$month, ref = "JAN") + cas2$bops*cas2$month + cas2$month_index + factor(cas2$summary))
summary(cas2_7)
AIC(cas2_7) #4126231
dwtest(cas2_7) #1.6125
anova(cas2_5, cas2_7, test = "Chisq") #Model fit improves with the interaction variable
bptest(cas2_7) #This model is heteroschedasticity


```


cas6
check data
```{r}
cas6$X <- NULL

dim(cas6)
str(cas6)
count(cas6, var = "bops")
count(cas6, var = "gender")
count(cas6, var = "ethnic_code")
count(cas6, var = "homeowner_code")

hist(cas6$net_purchase_amount)
hist(log(cas6$net_purchase_amount +1))
cas6$logamount <- log(cas6$net_purchase_amount +1)

hist(cas6$age_band)
hist(cas6$est_income_code)
hist(cas6$length_of_residence)

cor <- cbind(cas6[,c(5,12,13,16)])
cor <- na.omit(cor)
cor6 <- cor(cor)
vif(cor)

sum(is.na(cas6))
colSums(is.na(cas6))

#replace NA with mean for columns age_band, est_income_code, and length_of_residence
cas6$age_band[is.na(cas6$age_band)] <- mean(cas6$age_band, na.rm = TRUE)
cas6$est_income_code[is.na(cas6$est_income_code)] <- mean(cas6$est_income_code, na.rm = TRUE)
cas6$length_of_residence[is.na(cas6$length_of_residence)] <- mean(cas6$length_of_residence, na.rm = TRUE)

unique(cas6$homeowner_code)
cas6$homeowner_code <- sub("^$", "N", cas6$homeowner_code)

#Same for the gender
cas6$gender <- sub("^$", "U", cas6$gender)
unique(cas6$gender)

unique(cas6$child)
count(cas6$child)
cas6$child <- sub("^$", "U", cas6$child)

colSums(is.na(cas6))
```

```{r}

cas6_1 <- lm(logamount ~ factor(gender) + age_band + est_income_code + factor(ethnic_code) + length_of_residence + factor(child) + factor(homeowner_code) + relevel(month, ref = "JAN") + bops, data = cas6)
summary(cas6_1)
AIC(cas6_1) #375588.1
dwtest(cas6_1) #1.3813

#Add month_index and summary
cas6_2 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + factor(ethnic_code) + length_of_residence + relevel(factor(child), ref = "U") + relevel(factor(homeowner_code), ref = "O") + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_2)
AIC(cas6_2) #333180.2
dwtest(cas6_2) #1.5022

#Take out ethnic code
cas6_3 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + length_of_residence + relevel(factor(child), ref = "U") + relevel(factor(homeowner_code), ref = "O") + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_3)
AIC(cas6_3) #333287.5
dwtest(cas6_3) #1.5012

#put in ethnic code and take out child
cas6_4 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + factor(ethnic_code) + length_of_residence + relevel(factor(homeowner_code), ref = "O") + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_4)
AIC(cas6_4) #333213.4
dwtest(cas6_4) #1.5019

#put in child and take out homeowner
cas6_5 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + factor(ethnic_code) + length_of_residence + relevel(factor(child), ref = "U") + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_5)
AIC(cas6_5) #333181
dwtest(cas6_5) #1.5022

#Take out legnth of residence

cas6_6 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + factor(ethnic_code) + relevel(factor(child), ref = "U") + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_6)
AIC(cas6_6) #333179
dwtest(cas6_6) #1.5022

#Take out ethnic code
cas6_7 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + relevel(factor(child), ref = "U") + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_7)
AIC(cas6_7) #333287
dwtest(cas6_5) #1.5022

#Put in ethinic code and take out child
cas6_8 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + factor(ethnic_code) + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_8)
AIC(cas6_8) #333208.2
dwtest(cas6_8) #1.5019

#Based on cas6_6 quadratic age_band
plot(cas6$net_purchase_amount ,cas6$age_band)
cas6_9 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + I(age_band^2) + est_income_code + factor(ethnic_code) + relevel(factor(child), ref = "U") + relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas6)
summary(cas6_9)
AIC(cas6_9) #333180.1
#For store 6, quadratic age_band seems not that significant as store 2

#How about bops and summary
cas6_10 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + factor(ethnic_code) + relevel(factor(child), ref = "U") + relevel(month, ref = "JAN") + bops*factor(summary) + month_index, data = cas6)
summary(cas6_10)
AIC(cas6_10) #332859.3
dwtest(cas6_10) #this model has autocorrelation

#Bops and month
cas6_11 <- lm(logamount ~ relevel(factor(gender), ref = "U") + age_band + est_income_code + factor(ethnic_code) + relevel(factor(child), ref = "U") + relevel(month, ref = "JAN")*bops + bops + month_index + factor(summary), data = cas6)
summary(cas6_11)
AIC(cas6_11) #329265.3
dwtest(cas6_11) #this model has autocorrelation

#Although this model has autocorrelation, the results still give me some insight of how bops service worked.

```

cas5998
```{r}

cas5998$X <- NULL

dim(cas5998)
count(cas5998, var = "bops")
count(cas5998, var = "gender") #Most of the gender is na, should consider drop this variable
count(cas5998, var = "ethnic_code") #Same as gender
count(cas5998, var = "homeowner_code") #same as gender

#the transactions of store 5998 don't have that much customer attributes as other two stores

hist(cas5998$net_purchase_amount)
hist(log(cas5998$net_purchase_amount +1))
cas5998$logamount <- log(cas5998$net_purchase_amount +1)

hist(cas5998$age_band)
hist(cas5998$est_income_code)
hist(cas5998$length_of_residence)

cor <- cbind(cas5998[,c(5,12,13,16)])
cor <- na.omit(cor)
cor5998 <- cor(cor)
vif(cor)

sum(is.na(cas5998))
colSums(is.na(cas5998))


unique(cas5998$homeowner_code)
count(cas5998$homeowner_code)
cas5998$homeowner_code <- sub("^$", "N", cas5998$homeowner_code)

#Same for the gender
cas5998$gender <- sub("^$", "U", cas5998$gender)
unique(cas5998$gender)

unique(cas5998$child)
count(cas5998$child)
cas5998$child <- sub("^$", "U", cas5998$child)

colSums(is.na(cas5998))

```

Store 5998 modeling
Since I don't have customer attirbutes for most of the transaction, I can only run a simple regression model based on few variables
```{r}
cas5998_1 <- lm(logamount ~ relevel(month, ref = "JAN") + bops + month_index + factor(summary), data = cas5998)
summary(cas5998_1)
AIC(cas5998_1) #156990.4
dwtest(cas5998_1) #1.6571, autocorrelation

cas5998_2 <- lm(logamount ~ relevel(month, ref = "JAN")*bops + month_index + factor(summary), data = cas5998)
summary(cas5998_2)
AIC(cas5998_2) #156196.4
dwtest(cas5998_2) #1.6571, autocorrelation

cas5998_3 <- lm(logamount ~ relevel(month, ref = "JAN") + bops + month_index + factor(summary)*bops, data = cas5998)
summary(cas5998_3)
AIC(cas5998_3) #156039.9
dwtest(cas5998_3) 

```

#Interpretation
In general
store2: cas2_5
store6: cas6_6
store5998: cas5998_1
```{r}
summary(cas2_5)
summary(cas6_6)
summary(cas5998_1)

ca$logamount <- log(ca$net_purchase_amount +1)
intg <- c(6.252, 5.990, 6.4684)

intgr <- data.frame(intercepts = intg,
                       slopes = c(2.228e-01, 1.802e-01, -0.1511), store = c("2", "6", "5998"))

casub <- ca[sample(nrow(ca),10000),]
typeof(casub$logamount)


ggplot(data = casub, aes(x = bops, y = logamount, xlevels = 2)) +
  geom_abline(data = intgr, aes(slope = slopes, intercept = intercepts, colour = store) , size = 1) +
  geom_point(aes(group = store_number, colour = factor(store_number)), alpha = 0.2) +
  theme(axis.title.y=element_text(size=rel(1.2),vjust=0.2),
          axis.title.x=element_text(size=rel(1.2),vjust=0.2),
          axis.text.x=element_text(size=rel(1.3)),
          axis.text.y=element_text(size=rel(1.3)),
          text = element_text(size=13)) +
  theme(legend.position = "top") +
  scale_colour_brewer(palette="Set3") 


```

Different month has different impact
store2 <- cas2_7
store6 <- cas6_11
store5998 <- cas5998_2
```{r}
summary(cas2_7)
facgender <- as.factor(cas2$gender)
facchild <- as.factor(cas2$child)
fachome <- as.factor(cas2$homeowner_code)
facsummary <- as.factor(cas2$summary)
age2 <- cas2$age_band^2

cas2$age_band <- as.numeric(cas2$age_band)

cas2_7_e <- lm(formula = cas2$logamount ~ facgender+ age2 + cas2$est_income_code + 
    cas2$length_of_residence + facchild + cas2$bops * cas2$month + cas2$month_index + 
    facsummary)
summary(cas2_7_e)

cas2_7_1 <- lm(logamount ~ relevel(factor(gender), ref = "U") + 
    age_band + I(age_band^2) + est_income_code + 
    length_of_residence + factor(child)+ bops * month + month_index + 
    factor(summary), data = cas2)

summary(cas2_7_1)

interact_plot(cas2_7_1, pred = "bops", modx = "month", color.class = "Set3")



```














